\subsubsection{Flexibility}
\subsubsubsection{addPublication} The function is easily add different access channel of publication.
\subsubsubsection{changePublicationState} The function is to be able to make impartation in the state of publication of a research.
\subsubsubsection{modifyPublicationType} The function is flexible to adopt change in the publication type 
\subsubsubsection{diactivatePublicationType} The function is flexible to turn off (disengage) a publication.
\subsubsubsection{reactivatePublicationType} The function is flexible to restart a publication
\subsubsubsection{addPublicationType} The function is flexible to created and update publications

\subsubsection{Maintainability}
It should be easy to maintain the system in the future. To this end future developers should be able to easily understand the system, the technologies chosen for the system can be reasonably expected to be available for a longtime, and developers should be able to easily and relatively quickly change aspects of the functionality the system provides, and add new functionality to the system.

\subsubsubsection{addPublication} The function of maintaining the system to will rely on how the system is be manage and cared for.  It depend on the developer to
\subsubsubsection{changePublicationState} This function totally depend on the maintenance of the system 
\subsubsubsection{modifyPublicationType} This function totally depend on the maintenance of the system
\subsubsubsection{diactivatePublicationType} This function totally depend on the maintenance of the system
\subsubsubsection{reactivatePublicationType} This function totally depend on the maintenance of the system
\subsubsubsection{addPublicationType} This function totally depend on the maintenance of the system

\subsubsection{Scalability} The network round-trip which is outside the control of the System.
\subsubsubsection{addPublication} The architecture of the system is easily scaled to add publication research communities of several hundred researchers. 
\subsubsubsection{changePublicationState} The function of the system is easy to change publication usually within the scale

\subsubsection{Performance requirements}
It was very hard to measure the performance of the services provided by publication module accurately. The execution time of the code is used at this stage to measure the performance of the provided service of publication module.
\subsubsubsection{addPublication} The function add only text based information so the are not any performance issues.
\subsubsubsection{changePublicationState} The function add only text based information so the are not any performance issues.
\subsubsubsection{modifyPublicationType} The function add only text based information so the are not any performance issues.
\subsubsubsection{diactivatePublicationType} The function it is not sufffering form any performance issues as it only manupulate some state falg for diactivation of publication type.
\subsubsubsection{reactivatePublicationType} The function it is not sufffering form any performance issues as it only manupulate some state falg for reactivation of publication type.
\subsubsubsection{addPublicationType} The function add only text based information so the are not any performance issues.

\subsubsection{Security}
User data in every of the services provided by the publication modules it is not valided to be a ligit data or to be in the boands. Users can perform buffer averflwo to try to exploait the vulnerabilities.
